---
title: "lglasso"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction_of_lglasso_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



```{r setup}
library(lglasso)
```

There are two main functions in this package. The first one is $lglasso$ which can output a sparse network representing the precision matrix by maximizing the $l_1$ penalized likelihood function. The second function if $mle$, which can compute the maximum likelihood estimates of precision matrix and the correlation parameter $\tau$ for a given network structure produced from function $lglasso$.   

```{r}
##The sample data are subset of a larger longitudinal data set  from a clinical project. 
##There are 13 clusters  are involved in the sample data.
sample_data=lglasso:::sample_data
dim(sample_data)
sample_data[1:5,1:5]
#sample_data=as.matrix(sample_data)
```

#### Example 1: Heterogeneous model with dampening correlation. 
```{r}
a=lglasso(data = sample_data, rho = 0.7, heter=T, ty=2)
# Individual dampening rate:
round(a$tau,3)

#  Number of edge in the estimated network: 
(length(which(a$omega!=0))-ncol(a$omega))/2
#  Subnetwork:

a$omega[1:5,1:5]
# loglikelihood: 

a$ll

```


#### Example 2: Homogeneous model with dampening correlation. 
```{r}
b=lglasso(data = sample_data, rho = 0.7, heter=F,ty=2)
# Shared dampening rate
round(b$tau,3)
# Number of edge in the estimated network
(length(which(b$omega!=0))-ncol(b$omega))/2

# Subnetwork
b$omega[1:5,1:5]
# loglikelihood
b$ll


```


#### Example 3: Heterogeneous model with uniform correlation. 
```{r}
c=lglasso(data = sample_data, rho = 0.7, heter=T, ty=0)

# indvidual dampening rate

round(c$tau,3)

# Number of edge in the estimated network
(length(which(c$omega!=0))-ncol(c$omega))/2

# subnetwork
c$omega[1:5,1:5]
# loglikelihood 
c$ll
```


[1] Zhou, J., Gui, J., Viles, W.D., Chen, H., Madan, J.C., Coker, M.O., Hoen, A.G., 2021a. Identifying Microbial Interaction Networks Based on Irregularly Spaced Longitudinal 16S rRNA sequence data. https://doi.org/10.1101/2021.11.26.470159



[2] Friedman J., Hastie T., Tibshirani R. (2019)  Graphical Lasso: Estimation of Gaussian Graphical Models, Version: 1.11. https://CRAN.R-project.org/package=glasso. 

